Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-01 sec_results.tex
update on sec5

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corrmb.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. }
	\label{fig:PlotCorrMBHMT}
\end{figure}

@@

To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with minimum $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the ridge yield is maximum.

The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.

The ridge yield is inspected as a function of the leading track selection in Fig.~\ref{fig:RidgeYield_ESE}. As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively. }
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.}
	\label{fig:PlotDeltaPhiESE}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
	\label{fig:RidgeYield_ESE}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrmb.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. }
	\label{fig:PlotCorrMBHMT}
\end{figure}

@@

To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}. The ridge structures are still seen with the event scale selection. With the minimum $\it{p}_{\rm{T, Jet}}$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. The minimum requirement for $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ is 9 GeV/\it{c}\rm{} or 10 GeV/\it{c}\rm{}, respectively. }
	\label{fig:PlotCorrHMTSel}
\end{figure}

The one-dimensional $\Delta\varphi$ distribution with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield increases as the event scale increases by requiring higher $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$. The model comparisons are seen as blue line for PYTHIA8 + String Shoving and apricot line for PYTHIA8 default, respectively. The PYTHIA8 + String Shoving describes ridge yield with the selection. The PYTHIA8 default predict the ridge yield to be zero with the selection, which also tell there is little ignorable jet contamination. Both models well describe the away-side yield with the $\it{p}_{\rm{T, Jet}}$ selection and overestimates away-side yield with the $\it{p}_{\rm{T, Lead}}$ selection.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\it{p}_{\rm{T, Lead}}$(lower) or $\it{p}_{\rm{T, Jet}}$(upper) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in 0-0.1\% multiplicity class. The filled circles show measurement with ALICE. Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
	\label{fig:PlotDeltaPhiESE}
\end{figure}

The spectra of the ridge yield as function of the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) are shown in Fig.~\ref{fig:RidgeYield_ESE}. The spectra are compared with model predictions. 
The increases of ridge yield with the selections are observed and the model with PYTHIA8 + String Shoving underestimates the ridge yield. with the $\it{p}_{\rm{T, Jet}}$ selection. the model prediction with PYTHIA8 default still assures ignorable jet contamination.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
	\label{fig:RidgeYield_ESE}
\end{figure}
